Considering scale in multilayer animal social networks

### 2020-06-22 paper/manuscript.Rmd
add box 2 for conclusion questiosn
rm conclusion
outline discussion
note intro

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
associations to occur individuals must share space, and thus have overlapping
home ranges [@Vander_Wal_2013]. In the context of the social environment, home
range overlap is an example of how animals share space over coarser spatial and
temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of sociality, including social association and home range overlap, vary
predictably with social interaction [@Castles_2014;
@Farine_2015a]. We therefore define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a] and suggest the 
potential for adaptive variance in social relationships is also scale-dependent. 
<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
under the expectation that there is some scale at which variance is greatest, and presumably
it is this scale that has the greatest effect on fitness or other traits-->

@@

@@

@@

# Conclusion
Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. We
show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability. Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks which incorporated high resolution GPS telemetry data and spatial land cover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore, e.g., number of observations, sociality across space
and time, are ones that can be observed as has <!-- edit-->traditionally been done in
ethology. We highlight ways in which scale ought to be considered for both
observed and remotely-sensed data when building social networks. GPS telemetry 
data provides a link between large scale landscape properties and
fine scale social interactions as animal movement occurs across the landscape,
and when taken into account with multiple individuals<!-- edit--> can indicate association
patterns. Thus, a layer incorporating relocation data could be a great boon
linking spatial and social layer in multilayer networks.

Silk et al. (2018) summarized some key multilayer questions in animal behaviour
research. While these questions are important for linking animal behaviour and
multilayer networks, we summarize our perspectives on the future of multilayer
networks with an additional set of questions posed through the lens of spatial
ecology that are relevant to the promise and problem of scale in multilayer
networks:

@@

<!-- JWT: It think we need an ending thought or punch or something, not end it on a question. -->

>>>>

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
associations to occur individuals must share space, and thus have overlapping
home ranges [@Vander_Wal_2013]. In the context of the social environment, home
range overlap is an example of how animals share space over coarser spatial and
temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of sociality, including social association and home range overlap, vary
predictably with social interaction [@Castles_2014;
@Farine_2015a]. <!-- careful with this definition of social scale ..
social scale is the type of and specification/detail/definition of-->We therefore define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a] and suggest the 
potential for adaptive variance in social relationships is also scale-dependent. 
<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
under the expectation that there is some scale at which variance is greatest, and presumably
it is this scale that has the greatest effect on fitness or other traits-->

@@

<!-- 
outline

1. TODO intro

2. social scale. our results. possible extensions with HMM. observational of dif behaviours

3. habitat+social, implicit -> explicit, our results.

4. movement, 1 sent biolog

5. seasonality, time windows

6. number obs

7. from conclusions

box1: fitness
box2: extending qs

@@

<!-- this was conclusion -->
Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. We
show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability. Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks which incorporated high resolution GPS telemetry data and spatial land cover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore, e.g., number of observations, sociality across space
and time, are ones that can be observed as has <!-- edit-->traditionally been done in
ethology. We highlight ways in which scale ought to be considered for both
observed and remotely-sensed data when building social networks. GPS telemetry 
data provides a link between large scale landscape properties and
fine scale social interactions as animal movement occurs across the landscape,
and when taken into account with multiple individuals<!-- edit--> can indicate association
patterns. Thus, a layer incorporating relocation data could be a great boon
linking spatial and social layer in multilayer networks.
<!-- JWT: It think we need an ending thought or punch or something, not end it on a question. -->
<!-- this was conclusion -->

@@

# Box 2 
Silk et al. (2018) summarized some key multilayer questions in animal behaviour
research. While these questions are important for linking animal behaviour and
multilayer networks, we summarize our perspectives on the future of multilayer
networks with an additional set of questions posed through the lens of spatial
ecology that are relevant to the promise and problem of scale in multilayer
networks:

@@
